On the specific recursive structure of iterated parametricity

### 2025-10-12 paper/paper.tex
paper: skeleton progress

% These are renewed in tables, but let's define them now for in-document
% typesetting
\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][][#2][][]}
\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][][#2][][]}
\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][][#2][][]}
\newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\newcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
\newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
\newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
\newcommandx{\cohp}{\coh{painting}[][][][][][][][]}
\newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}

@@

Formally, this can be described as:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \framep[n][0,...,p]           &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n][0,...,p-1]   \\
                    \painting[n][0,...,p-1] \\
                  \end{array}\right)                                              \\
              \end{array}\right) : \frametype[n][0,...,p]
    }                                                                       \\
    \framep[n][0]                 &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)        & \defeq & (\unitpoint,unit)            \\
    \framep[n][0,...,p+1]         &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
              \restrf[n][0,...,p]   \\
            \end{array}\right)      & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][0,...,p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right)     ,                     \\
              \Sigma d:\framep[n+1][0,...,p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right).\,                     \\
              \quad \Pi\omega.\,\painting[n][p](\restrf[n][p](d)) \\
            \end{array}\right) \\
    \restrftype[n][0,...,p-1]     &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
              \end{array}\right) : Type_{l}
    }                                                                       \\
    \restrftype[n][0,...,0-1]     &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)        & \defeq &
    \unittype                                                               \\
    \restrftype[n][0,...,(p+1)-1] &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
            \end{array}\right)      & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n+1][0,...,p-1]
      :\restrftype[n+1][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
              \end{array}\right)                         .  \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
                \restrf[n+1][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array}      \\
  \end{array}
\end{equation*}

@@

This allows to define $\painting[n][p]$ formally:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]              &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                  \end{array}\right)                                                  \\
                \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                    \framep[n-1][p,...,n-2]   \\
                    \painting[n-1][p,...,n-2] \\
                    \restrf[n][0,...,p-1]     \\
                  \end{array}\right)                                                  \\
                E:\framep[n-1][n-1]\rightarrow Type_l                                            \\
              \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
    }                                                            \\
    \painting[n][n]              &
    \left(\begin{array}{l}
              \framep[n-1][0,...,n-1]   \\
              \painting[n-1][0,...,n-1] \\
              \unitpoint                \\
              \unitpoint                \\
              \restrp[n][0,...,n-1]     \\
              \unitpoint                \\
              E                         \\
            \end{array}\right) & \defeq & E                        \\
    \painting[n][p](p<n)         &
    \left(\begin{array}{l}
              \framep[n-1][0,...,p-1]   \\
              \painting[n-1][0,...,p-1] \\
              \framep[n-1][p,...,n-1]   \\
              \painting[n-1][p,...,n-1] \\
              \restrf[n][0,...,p-1]     \\
              \restrf[n][p,...,n-1]     \\
              E                         \\
            \end{array}\right) & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
              \painting[n-1][0,...,p](\restrf[n][p](d))). \\
              \painting[n][p+1,...,n-1]
              \left(\begin{array}{l}
                  \framep[n-1][0,...,p]       \\
                  \painting[n-1][0,...,p]     \\
                  \framep[n-1][p+1,...,n-1]   \\
                  \painting[n-1][p+1,...,n-1] \\
                  \restrf[n][0,...,p]         \\
                  \restrf[n][p+1,...,n-1]     \\
                  E                           \\
                \end{array}\right)(d,l)           \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

>>>>

% These are renewed in tables, but let's define them now for in-document
% typesetting
\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\newcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
\newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
\newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
\newcommandx{\cohp}{\coh{painting}[][][][][][][][]}
\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}

\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
\newcommandx{\layertype}[2][1,2]{\prim{layertype}[][#1][#2][][]}
\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
\newcommandx{\restrltype}[2][1,2]{\prim{restrltype}[][#1][#2][][]}
\newcommandx{\restrptype}[2][1,2]{\prim{restrptype}[][#1][#2][][]}
\newcommandx{\cohftype}[2][1,2]{\prim{cohftype}[][#1][#2][][]}
\newcommandx{\cohltype}[2][1,2]{\prim{cohltype}[][#1][#2][][]}
\newcommandx{\cohptype}[2][1,2]{\prim{cohptype}[][#1][#2][][]}

\newcommandx{\deps}[2][1,2]{\prim{deps}[][#1][#2][][]}
\newcommandx{\extradeps}[2][1,2]{\prim{deps}[][#1][#2][][]}
\newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
\newcommandx{\extradepstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                       \\
    \frametype[n][]           &                                              & \defeq & \unittype                                                                                        \\
    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n+1][0,...,p-1] \times Type_l                                                         \\
    \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                       \\
    \paintingtype[n][]        & \unitpoint                                   & \defeq & \unittype                                                                                        \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n+1][0,...,p-1](\framep[n+1][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
    \layertype[n][p]          & \framep[n][p]                                & :      & Type_{l+1}                                                                                       \\
  \end{array}
\end{equation*}

Formally, this can be described as:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \framep[n][0,...,p]           &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n][0,...,p-1]   \\
                    \painting[n][0,...,p-1] \\
                  \end{array}\right)                                              \\
              \end{array}\right) : \frametype[n][0,...,p]
    }                                                                  \\
    \framep[n][0]                 &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)        & \defeq & (\unitpoint,unit)       \\
    \framep[n][0,...,p+1]         &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
              \restrf[n][0,...,p]   \\
            \end{array}\right)      & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][0,...,p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right), \\
              \Sigma d:\framep[n+1][0,...,p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right).\, \\
              \quad \layer[n][p]
              \left(\begin{array}{l}
                  \framep[n+1][0,...,p-1]   \\
                  \painting[n+1][0,...,p-1] \\
                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right) \\
            \end{array}\right)                   \\
    \restrftype[n][0,...,p-1]     &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
                \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
              \end{array}\right) : Type_{l}
    }                                                                  \\
    \restrftype[n][0,...,0-1]     &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)        & \defeq &
    \unittype                                                          \\
    \restrftype[n][0,...,(p+1)-1] &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
            \end{array}\right)      & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n+1][0,...,p-1]
      :\restrftype[n+1][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
              \end{array}\right)                         .  \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
                \restrf[n+1][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array} \\
    \layer[n][p]                  &
    \left(\begin{array}{l}
              \framep[n][0,...,p]     \\
              \painting[n][0,...,p]   \\
              \restrf[n+1][0,...,p-1] \\
            \end{array}\right)    & \defeq &
    \Pi\omega.\,\painting[n][p](\restrf[n][p](d))
  \end{array}
\end{equation*}

At this stage, it is convenient to use an abbreviation to combine a $\framep$, a $\painting$ and a $\restrf$ in one block, which we call deps:

\begin{align*}
  \deps[n][0,..,p-1] \defeq
  \left(\begin{array}{l}
            \framep[n][0,...,p-1] :\frametype[n][0,...,p-1]      \\
            \painting[n][0,...,p-1] :\paintingtype[n][0,...,p-1] \\
            \restrf[n][0,...,p-1]  :\restrftype[n][0,...,p-1]    \\
          \end{array}\right)
\end{align*}
so that $\framep[n][0,...,p]$ has type $\deps[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$.

@@

At this stage, it is also convenient to use an abbreviation to combine the extra parts of $\framep$, a $\painting$ and a $\restrf$ in one block, which we call $\extradeps[n][p,...,n-1]$:

\begin{align*}
  \extradeps[n][p,..,n-1] (\deps[n][0,...,p-1]) \defeq
  \left(\begin{array}{l}
            \framep[n][p,...,n-1] :\frametype[n][p,...,n-1]      \\
            \painting[n][p,...,n-1] :\paintingtype[n][p,...,n-1] \\
            \restrf[n][p,...,n-1]  :\restrftype[n][p,...,n-1]    \\
          \end{array}\right)
\end{align*}

This allows to define $\painting[n][p]$ formally:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]              &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \deps[n-1][0,...,p-1]:\depstype[n-1][0,...,p-1]                                \\
                \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                             \\
                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\deps[n-1][p,...,n-1]) \\
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                  \end{array}\right)                                                \\
                \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
                \left(\begin{array}{l}
                    \deps[n-1][0,...,p-1]     \\
                    \framep[n-1][p,...,n-2]   \\
                    \painting[n-1][p,...,n-2] \\
                  \end{array}\right)                                                \\
                E:\framep[n-1][n-1]\rightarrow Type_l                                          \\
              \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
    }                                                            \\
    \painting[n][n]              &
    \left(\begin{array}{l}
              \framep[n-1][0,...,n-1]   \\
              \painting[n-1][0,...,n-1] \\
              \unitpoint                \\
              \unitpoint                \\
              \restrp[n][0,...,n-1]     \\
              \unitpoint                \\
              E                         \\
            \end{array}\right) & \defeq & E                        \\
    \painting[n][p](p<n)         &
    \left(\begin{array}{l}
              \framep[n-1][0,...,p-1]   \\
              \painting[n-1][0,...,p-1] \\
              \framep[n-1][p,...,n-1]   \\
              \painting[n-1][p,...,n-1] \\
              \restrf[n][0,...,p-1]     \\
              \restrf[n][p,...,n-1]     \\
              E                         \\
            \end{array}\right) & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
              \painting[n-1][0,...,p](\restrf[n][p](d))). \\
              \painting[n][p+1,...,n-1]
              \left(\begin{array}{l}
                  \framep[n-1][0,...,p]       \\
                  \painting[n-1][0,...,p]     \\
                  \framep[n-1][p+1,...,n-1]   \\
                  \painting[n-1][p+1,...,n-1] \\
                  \restrf[n][0,...,p]         \\
                  \restrf[n][p+1,...,n-1]     \\
                  E                           \\
                \end{array}\right)(d,l)           \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

\section{...}

We can now define the types of sequences of $\framep$ and $\painting$ as follows:

to do : def of restrptype

Mutual definition of \restrf and cohframetype

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrf[n][0,...,p]                                                           &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \deps[n][0,...,p-2]:\depstype[n][0,...,p-2]                                \\
                \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
                \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \deps[n][0,...,p-1]      \\
                    \extradeps[n][p-1,...,n] \\
                  \end{array}\right)                                             \\
                \cohf[n][0,...,p]:\cohftype[n][0,...,p]
              \end{array}\right) : \restrftype[n][0,...,p]
    }                                                                                                                                                         \\
    \restrf[n][0]                                                                 &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)                                                        & \defeq & (\unitpoint,\lambda q. \lambda\epsilon. \lambda \_.\unitpoint) \\
    \restrf[n][0,...,p+1]                                                         &
    \left(\begin{array}{l}
              \deps[n][0,...,p]        \\
              \extradeps[n][p-1,...,n] \\
              \restrp[n][0,...,p]      \\
              \cohf[n][0,...,p]        \\
            \end{array}\right)                                                   & \defeq &
    \begin{array}{l}
      \restrf[n+1][0,...,p]
      \left(\begin{array}{l}
                \deps[n+1][0,...,p-1]    \\
                \extradeps[n][p-1,...,n] \\
                \restrp[n+1][0,...,p-1]  \\
                \cohf[n+1][0,...,p-1]    \\
              \end{array}\right)     ,                                            \\
      \lambda q.\lambda \epsilon.\lambda (\framep[n+1][0,...,p], \layer[n][p]). \\
      \left(\restrf[n][0,...,p]
      \left(\begin{array}{l}
                  \deps[n+1][0,...,p-1]    \\
                  \extradeps[n][p-1,...,n] \\
                  \restrp[n+1][0,...,p-1]  \\
                  \cohf[n+1][0,...,p-1]    \\
                \end{array}\right), \restrl[n][p](...)(l)\right)                    \\
    \end{array}                                                                  \\
    \cohftype[n][0,...,p-1]                                                       &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \deps[n][0,...,p-1]:\depstype[n][0,...,p-1]                                \\
                \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
                \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1])       \\
              \end{array}\right) : Type_{l}
    }                                                                                                                                                         \\
    \cohftype[n][0,...,0-1]                                                       &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)                                                        & \defeq &
    \unittype                                                                                                                                                 \\
    \cohftype[n][0,...,(p+1)-1]                                                   &
    \left(\begin{array}{l}
              \deps[n][0,...,p]        \\
              \extradeps[n][p-1,...,n] \\
              \restrp[n][0,...,p]      \\
            \end{array}\right)                                                   & \defeq &
    \begin{array}{l}
      \Sigma \cohf[n+1][0,...,p-1]
      :\cohftype[n+1][0,...,p-1]
      \left(\begin{array}{l}
                \deps[n+1][0,...,p-1]    \\
                \extradeps[n][p-1,...,n] \\
                \restrp[n+1][0,...,p-1]  \\
              \end{array}\right)                         .     \\
      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega. \\
      \restrf[n][p][q][\epsilon](\restrf[n+1][p][r][\omega]
      \left(\begin{array}{l}
                \deps[n+1][0,...,p-1]    \\
                \extradeps[n][p-1,...,n] \\
                \restrp[n+1][0,...,p-1]  \\
              \end{array}\right)(d)) =                         \\
      \restrf[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon]
      \left(\begin{array}{l}
                \deps[n+1][0,...,p-1]    \\
                \extradeps[n][p-1,...,n] \\
                \restrp[n+1][0,...,p-1]  \\
              \end{array}\right)(d))                         \\
    \end{array}                                                                                     \\
    \restrl[n][p][q][\epsilon]                                                    &
    \left(\begin{array}{l}
              \deps[n][0,...,p]:\depstype[n][0,...,p]                                    \\
              \extradeps[n][p-1,...,n]:\extradepstype[n][0,...,p-2](\deps[n][0,...,p-1]) \\
              \cohf[n][0,...,p]:\cohftype[n][0,...,p]                                    \\
              \layer[n+1][p]:\layertype[n+1][p]                                          \\
            \end{array}\right) & :      &
    \layer[n][p]                                                                                                                                              \\
    \restrl[n][p][q][\epsilon]                                                    &
    \left(\begin{array}{l}
              \deps[n][0,...,p]        \\
              \extradeps[n][p-1,...,n] \\
              \cohf[n][0,...,p]        \\
              \layer[n][p]             \\
            \end{array}\right)                                                   & \defeq &
    \lambda\omega.\,\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega]}{\restrp[n][p](\layer[n][p])}                                                         \\
  \end{array}
\end{equation*}
